---
title: "Weight of Fish"
author: "Tyler Frasier"
date: "`fall 2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
fish = read_csv("Fish.csv")
```

# Predicting Fish Weight
Find the best model using 2 variables to predict Perch weight, and compare this to the best overall model. 


## Perch

```{r}
perch = filter(fish, Species == 'Perch')
```

### Best Models

### Best Two regressor model


```{r}
modelperch = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = perch, )
summary(modelperch)
```


## Best two variable equation 

Weight = -536 + 74.77*Height + 69.62*Width

## Pike

```{r}
Pike = filter(fish, Species == 'Pike')
```

## Best Model Rogressor

```{r}
modelPike = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Pike, )
summary(modelPike)
```

```{r}
bestPike = lm(Weight ~ Length1 + Length3, data = Pike)
summary(bestPike)
```



### Best Two variable equation

Weight = -1675.79 + -105.64*Length1 + 141.25*Length3



## Roach

```{r}
Roach = filter(fish, Species == 'Roach')
```

### Best Two regressor model

```{r}
modelRoach = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = Roach, )
summary(modelRoach)
```

```{r}
bestRoach = lm(Weight ~ Width + Length3, data = Roach)
summary(bestRoach)
```










## Roach

### Best Models

### Best Two variable equation

Weight = -319.188 + 72.300*Width + 8.278*Length3

## Final Summary Statements

The best models using two variable to predict Perch weight, are Height & Width. 

The best model using 2 variables to predict Pike weight, are Length1 and Length3 models.

The best model using 2 variables to predict Roach weight, are Width and Length3.